Modern BTree\\ techniques

### 2020-01-12 btree/presentation.tex
interpolation search

%\newcommand\tikzmark[1]{%
  %\tikz[overlay,remember picture] \coordinate (#1);}

@@

>>>>

\def\strongdata{strong_correlation.data}
\def\weakdata{weak_correlation.data}

@@

    \end{center}
\end{frame}
\note{
    OrientDB uses SB-Tree, but are they the same?
}

    \begin{center}
    \textbf{Interpolation search}
    \vspace{1cm}

    \begin{overprint}[12cm]
        \onslide<1>
        \begin{center}
        \begin{tikzpicture}[]
            \node[draw] (key1) {5};
            \foreach \i / \value [evaluate=\i as \prev using \i-1] in
                {2/9,3/12,4/16,5/19,6/21,7/25,8/27,9/31,10/34,11/36}
            {
                \node[draw, right=0 of key\prev] (key\i) {\value};
            }
        \end{tikzpicture}
        \end{center}

        \onslide<2>
        \begin{center}
        \begin{tikzpicture}[]
            \node[draw] (key1) {5};
            \foreach \i / \value [evaluate=\i as \prev using \i-1] in
                {2/9,3/12,4/16,5/19,6/21,7/25,8/27,9/31,10/34,11/36}
            {
                \node[draw, right=0 of key\prev] (key\i) {\value};
            }

            \coordinate[below=1cm of key1] (start);
            \draw[->, btree-line] (start.south)
                .. controls ([xshift=1cm] start) and ([yshift=-1cm] key6) ..
                (key6.south);
            \draw[->, btree-line] (key6.south)
                .. controls ([yshift=-1cm] key6) and ([yshift=-1cm] key9) ..
                (key9.south);
            \draw[->, btree-line] (key9.south)
                .. controls ([yshift=-0.9cm] key9) and ([yshift=-0.9cm] key10) ..
                (key10.south);

        \onslide<3>
        \begin{center}
        \begin{tikzpicture}[xscale=0.6, yscale=0.1]
            \draw[->] (0,0) -- (11,0);
            \draw[->] (0,0) -- (0,36);
            \draw[color=red, line width=2pt] plot[id=x] file {\strongdata};
        \end{tikzpicture}
        \end{center}

        \onslide<4>
        \begin{center}
        \begin{tikzpicture}[]
            \node[draw] (key1) {5};
            \foreach \i / \value [evaluate=\i as \prev using \i-1] in
                {2/9,3/12,4/16,5/19,6/21,7/25,8/27,9/31,10/34,11/36}
            {
                \node[draw, right=0 of key\prev] (key\i) {\value};
            }

            \coordinate[below=1cm of key6] (start);
            \draw[->, btree-line] (start.south)
                .. controls ([xshift=1cm] start) and ([yshift=-1cm] key10) ..
                (key10.south);

        \onslide<5>
        \begin{center}
        \begin{tikzpicture}[]
            \node[draw] (key1) {5};
            \foreach \i / \value [evaluate=\i as \prev using \i-1] in
                {2/6,3/15,4/15,5/16,6/43,7/95,8/96,9/97,10/128,11/499}
            {
                \node[draw, right=0 of key\prev] (key\i) {\value};
            }

        \onslide<6>
        \begin{center}
        \begin{tikzpicture}[xscale=0.6, yscale=0.008]
            \draw[->] (0,0) -- (11,0);
            \draw[->] (0,0) -- (0,499);
            \draw[color=red, line width=2pt] plot[id=x] file {\weakdata};
        \end{tikzpicture}
        \end{center}
    \end{overprint}
